---
title: "Asian American College Access"
subtitle: "Midpoint Presentation"
author: "Jonathon Sun"
date: "2/8/2022"
Bibliography: "references.bib"
output: 
  ioslides_presentation:
    widescreen: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

```{r loading data, include=FALSE}
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

# Data Import and Cleaning --------------------------------
source("Data/ShapeFiles.R")
source("Data/SafeGraph.R")
source("Data/Census_Data.R")
source("Data/ACS_Cluster.R")
source("Data/Gmaps_Locations.R")
source("Data/IPEDS_DATA.R")
source("Data/Carnegie_Classification.R")
source("Data/Philly_School_metrics.R")
source("Data/GTFS_Data.R")
source("Data/Knn.R")

#Analysis
source("Data_Analysis/Summary_Stats.R")
source("Data_Analysis/Morans_I.R")
source("Data_Analysis/K-clustering.R")

# Figures -----------------------------
source("Plots/Presentation_Figures.R")
```

# Introduction

## Introduction

<div style = "float: left; width: 40%">
Asian American comprises a panoply of differing and unique intersectional identities, histories, and experiences, yet Asian Americans are essentialized as a group and broadly stereotyped as the model minority, which shapes information to college access and campus resources (Museus & Truong, 2009; Palmer & Maramba, 2015; Poon & Byrd, 2013). 
</div>

<div style = "float: right; width: 60%">
```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(Asian_Pop_Philly)
Fig_1
```
</div>

## Research Question

What kind of educational environments do different Asian American groups exist in?

  - Is there spatial clustering of Asian Americans based on more specific ethnic-racial category?
  - How are access to educational resources spatially distributed from different Asian American ethnic-racial groups?

## Bodies of Literature

<div style = "float: left; width: 50%">

**Theories on Urban Spaces**

  - Formations of Cities
  - Subgroup culture in Urban Spaces
  
**Asian Americans**

  - Asian American History
  - Geographic Differences
  
</div>
  
<div style = "float: right; width: 50%">
**Globalization of Higher Education**

  - Immigration patterns
  - Race across Transnational Lines
  
**College Access Frameworks**
  
  - College Deserts and College Oasis
  - Resistance and Fortressing Geographies

</div>

# Framework

## Critical Geographic College Access (CGCA) 

<div style = "float: left; width: 50%">

**Hillman (2016)**

Individual choices to go to college are shaped by their geographic context, which constrains the options of school context, community context, and their social habitus.

</div>


<div style = "float: right; width: 50%">

**Dache-Gerbino (2016)**

Critical Geographic College Access (CGCA) framework to visually show how urban development and modernization failed black communities and that locations of colleges are not just coincidences but socially constructed around a history of residential segregation. 

</div>

# Methods

## Methods
 - Spatial Autocorrelation
      - local Moran's I
 - Nearest Neighbor Analysis
      - University
      - Tutoring Services
      - K-12 Schools that need intervening
 - K-Cluster Analysis

## Spatial Autocorrelation



## Nearest Neighbor Analysis

## K-cluster Analysis

# Exploratory Data Analysis | Enrollment
Data on enrollment in Higher Education

## Overall Enrollment in Higher Education {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(Enrollment_time)
Fig_1

```

## Overall Enrollment in Higher Education {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(PoC_Enrollment_Time) 
Fig_1
```

## Enrollment by Carnegie Classification {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=10}
Fig_1 <- plotly_build(Enrollment_time_Facet_Race)
Fig_1
```
# Exploratory Data Analysis | Census Data

## Race Over Time {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(Race_Frequency_Philly)
Fig_1
```

## Graphing Change Over Time {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(figure2_slides)
Fig_1
```

## Asian Ethnic {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(Asian_Pop_Philly)
Fig_1
```

# Exploratory Data Analysis | Geographic Contexts 

## Geographic Contexts | K-12 Education Landscape {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.asp=.62, fig.width=8}
Education_Institutions
```

## Geographic Contexts | Higher Education Landscape {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Higher_Education_Institutions
```

# Methods of Analysis

## Potential quantitative Methods

**1. Moran's I**

Use Moran's I to show how populations are clustered in Philadelphia

**2. K-Cluster Analysis**

Show how schools are clustered around particular areas of the city

**3. Some form of Regression**

Very open to suggestions and methods

# Next Steps | Reviewing Literature

## Next Steps
Clustering and Moran's I are the first steps before conducting more analysis. 

**Reviewing Literature**
Based on some of the literature, I will continue to refine my research question based on what else has been done in the literature.
