---
title: "Asian American College Access"
author: "Jonathon Sun"
date: "2/8/2022"
output: 
  ioslides_presentation:
    widescreen: true
---

```{r setup, include=FALSE}

pacman::p_load(plotly, tidyverse, DT, ggplot, sf, formattable)

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

# Data Import and Cleaning --------------------------------
source("Data/ShapeFiles.R")
source("Data/SafeGraph.R")
source("Data/Census_Data.R")
source("Data/Gmaps_Locations.R")
source("Data/IPEDS_DATA.R")
source("Data/Carnegie_Classification.R")
source("Data/Timeline.R")

# Figures -----------------------------
source("Plots/Presentation_Figures.R")
```

# Introduction

Asian Americans 


## Research Project Context

This study is part of a larger mixed methods project. 

  - Qualitative portion: How are College Access experiences similar or different for Asian Americans of different ethnic backgrounds
  
  - Quantitative portion: What is the geographic context of residents? What environmental factors shape Higher Education attainment for Asian Americans?

## Current Research Timeline {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
timeline
```

## Bodies of Literature

<div style = "float: left; width: 50%">

**Theories on Urban Spaces**

  - Formations of Cities
  - Subgroup culture in Urban Spaces
  
**Asian Americans**

  - Asian American History
  - Geographic Differences
  
</div>
  
<div style = "float: right; width: 50%">
**Globalization of Higher Education**

  - Immigration patterns
  - Race across Transnational Lines
  
**College Access Frameworks**
  
  - College Deserts and College Oasis
  - Resistance and Fortressing Geographies

</div>

## Datasets
- American Community Survey (ACS5 year)
  - Using `tidycensus` package to access the data.
  - Using data from 2011 - 2019
- Integrated Postsecondary Education Data System (IPEDS)
  - Pulled from their website
- SafeGraph
  - Data of all places labelled as education
- Carnegie Classifications
  - Includes classifications such as large research university
- Open Transit Planner (OTP)
  - Uses General Transit Feed Specifications (GTFS) to estimate travel times 

# Exploratory Data Analysis | Enrollment
Data on enrollment in Higher Education

## Overall Enrollment in Higher Education {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(Enrollment_time)
Fig_1

```

## Overall Enrollment in Higher Education {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(PoC_Enrollment_Time) 
Fig_1
```

## Enrollment by Carnegie Classification {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=10}
Fig_1 <- plotly_build(Enrollment_time_Facet_Race)
Fig_1
```
# Exploratory Data Analysis | Census Data

## Race Over Time {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(Race_Frequency_Philly)
Fig_1
```

## Graphing Change Over Time {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(figure2_slides)
Fig_1
```

## Asian Ethnic {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Fig_1 <- plotly_build(Asian_Pop_Philly)
Fig_1
```

# Exploratory Data Analysis | Geographic Contexts 

## Geographic Contexts | K-12 Education Landscape {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.asp=.62, fig.width=8}
Education_Institutions
```

## Geographic Contexts | Higher Education Landscape {.flexbox .vcenter}

```{r echo=FALSE, message=FALSE, warning=FALSE}
Higher_Education_Institutions
```

# Methods of Analysis

## Potential quantitative Methods

**1. Moran's I**

Use Moran's I to show how populations are clustered in Philadelphia

**1. K-Cluster Analysis**

Show how schools are clustered around particular areas of the city

**1. Some form of Regression**

Very open to suggestions and methods

# Next Steps | Reviewing Literature

## Next Steps
Clustering and Moran's I are the first steps before conducting more analysis. 

**Reviewing Literature**
Based on some of the literature, I will continue to refine my research question based on what else has been done in the literature.
