---
title: "Untitled"
author: "Jonathon Sun"
date: "2/8/2022"
output: 
  ioslides_presentation:
    widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown
<div class = "columns-2">
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

</div>
## Slide with Bullets

<div style = "float: left; width: 50%">

**Theories on Urban Spaces**

  - Formations of Cities
  - Subgroup culture in Urban Spaces
  
**Asian Americans**

  - Asian American History
  - Geographic Differences
  
</div>
  
<div style = "float: right; width: 50%">
**Globalization of Higher Education**

  - Immigration patterns
  - Race across Transnational Lines
  
**College Access Frameworks**
  
  - College Deserts and College Oasis
  - Resistance and Fortressing Geographies

</div>


## Datasets
- American Community Survey (ACS5 year)
  - Using `tidycensus` package to access the data.
  - Using data from 2011 - 2019
- Integrated Postsecondary Education Data System (IPEDS)
  - Pulled from their website
- SafeGraph
- Carnegie Classifications


## Slide with R Output

This study is part of a larger mixed methods project. 

  - Qualitative portion: How are College Access experiences similar or different for Asian Americans of different ethnic backgrounds
  
  - Quantitative portion: What is the geographic context of residents? What environmental factors shape Higher Education attainment for Asian Americans?
  
## Slide with Plot

```{r pressure}
plot(pressure)
```

